Figure 1. Microbiome abundances

### 2021-10-13 reports/rmarkdown/manuscript/Figure1.Rmd

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(RColorBrewer)
  remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

@@

#i <- ASV[2]
ASV <- list(c("Luminal_gr","ASV_CVL_V3_normalized_batch_corrected"),
         c("Tissue_gr","ASV_tissue_V3_normalized_batch_corrected")
          #"3"="ASV_CVL_V2_normalized_NOT_batch_corrected"
         )
for(i in ASV){
  x <- datasets_all_samples[[i[2]]]
  gr <- factor(setNames(metadata[[i[1]]],metadata$ID))
  #x <- x[,sample_use]
  #x <- datasets_all_samples[[2]]

@@

  shann <- vegan::diversity(t(temp),index = c("shannon") )
  simp <- vegan::diversity(t(temp),index = c("simpson") )
  invsimp <- vegan::diversity(t(temp),index = c("invsimpson") )
  divers <- as.matrix(rbind(shann,simp,invsimp) )
  divers[is.infinite(divers)] <- 0
  rownames(divers) <- c("Shannon","simpson","Inv Simpson")
  barlist( data = divers[,order(group_annotation)],
         main = "", xlab="", #bg="white", #cex=.6, 
         genes = c("Shannon","simpson","Inv Simpson"),
         # clustering = group_annotation,
         draw_mean_lines=F,col = pal[gr[order(group_annotation)]])

@@

}
### C
############################
# TOTAL RELATIVE ABUNDANCE #
############################
TRX <- datasets_all_samples[["Tissue_RNAseq_V3_normalized"]]
sample_use <- colnames(TRX)[colSums(TRX)!=0]
raw <- c("ASV_CVL_V3", "ASV_tissue_V3") %>% set_names()

>>>>

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(RColorBrewer)
  remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

#i <- ASV[2]
ASV <- list(c("Luminal_gr","ASV_CVL_V3_normalized_batch_corrected"),
         c("Tissue_gr","ASV_tissue_V3_normalized_batch_corrected")
          #"3"="ASV_CVL_V2_normalized_NOT_batch_corrected"
         )
div_list <- list()
for(i in ASV){
  x <- datasets_all_samples[[i[2]]]
  gr <- factor(setNames(metadata[[i[1]]],metadata$ID))
  #x <- x[,sample_use]
  #x <- datasets_all_samples[[2]]

@@

  shann <- vegan::diversity(t(temp),index = c("shannon") )
  simp <- vegan::diversity(t(temp),index = c("simpson") )
  invsimp <- vegan::diversity(t(temp),index = c("invsimpson") )
  divers <- as.matrix(rbind(shann,simp,invsimp) )
  divers[is.infinite(divers)] <- 0
  rownames(divers) <- c("Shannon","Simpson","Inv Simpson")

  div <- tibble(shann, simp, invsimp ) %>% rename_with(., ~paste0(c("Shannon","Simpson","Inv Simpson")))
  div_list[[length(div_list) + 1]] <- div

  barlist( data = divers[,order(group_annotation)],
         main = "", xlab="", #bg="white", #cex=.6, 
         genes = c("Shannon","Simpson","Inv Simpson"),
         # clustering = group_annotation,
         draw_mean_lines=F,col = pal[gr[order(group_annotation)]])

@@

}

# save diversity index stats
div_stat <- div_list %>% 
  set_names(map(ASV,1)) %>%
  map(., ~summarise_all(.x, list(median=median, IQR=IQR), na.rm = TRUE)) %>%
  map(., ~pivot_longer(.x, everything(), names_sep = "_", names_to = c(".value", "Stats"), )) %>%
  bind_rows(.id = "Sample type") %>%
  mutate("Sample type" = gsub("_gr", "", .$"Sample type"))

write.xlsx(div_stat, file=paste0("../../../results/","Suppl.Tbl.1 Diversity statistics",".xlsx"))

### C
############################
# TOTAL RELATIVE ABUNDANCE #
############################
TRX <- datasets_all_samples[["Tissue_RNAseq_V3_normalized"]]
sample_use <- colnames(TRX)[colSums(TRX)!=0]
raw <- c("ASV_CVL_V3", "ASV_tissue_V3") %>% set_names()
